I am glad that you, my dear reader, decided to read this little article I made about some topics I like.
First and foremost, it's crucial for me to explain to you, the reader, about a little bit
of my life, as it might help understand better the topics that will be covered in the next
chapters.

You can call me Mont. I am not academically inclined towards philosophy nor theology, I am a biologist
by profession. My first language is not english, therefore expect some bad grammar, although I will
try my best to keep it formal and understandable.

In relation to the content of this article, we will not be talking about my experiences nor anything of
that sort, although I might be giving some commentaries and opinions on the topics presented. This
article is an attempt at formalizing my thoughts on idealism, animism, and paganism, as well as the
relationships that each of them have with each other.

Lastly, I will be giving a brief overview of the chapters to come. As it might be noticeable (if you saw
the table of contents), the article follows, more or less, the format of the plot of a "narrative": it has
the start of the story, the exposition of the conflicts, the action with climax, and then the resolution.

On the definitions chapter, we are going to be exploring the divergent definitions given to each of
the terms (idealism, animism, paganism). After that is done, we are going to choose the one definition
(for each of the terms) that will continue to be used on this article.

Next, we will go through each of the ideas, one by one, comparing them with the previous ones discussed.
The last chapter, final thoughts, is the conclusion chapter, showing everything that was talked
about in a very compressed way.

Now it's time for us to travel on this journey together. I hope you learn something new and, hopefully,
have fun reading. Ready, set, go!